---
title: "flowmalizR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{flowmalizR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

Flowmalizr takes an xls input sheet containing columns listed as groups, total_cell_count_per_mL, live_cells, and phenotypes of interest. Each row contains 
a group-replicate, cell number per mL, live cell count, and cells identified, 
respectively. This is used to detemine cells_from_total and percentage of total by (total_cell_count_per_mL*cells-of-phenotype/live_cells)*100. The output from this 
function is a dataframe that can be manipulated for visualization of cell phenotypes 
from each group








### Load `flowmalizr()`
```{r setup}
library(flowmalizr)
```
### Read in the raw file and name it as `path_to_data`
```{r}
path_to_data <- system.file("extdata", "example_data.xlsx", package = "flowmalizr")

flowmalizr(path = path_to_data)
```
### Separate group and replicate into their own columns
```{r}
#sep_groups()
```
### Pull unique gated populations
```{r}
#unique_pops()
```
### View all phenotype's in each group
```{r}
#gg_view_all()
```
### Plot percentage of populations per group
```{r}
#visualize_groups()
```
### 1v1 comparison: enter two groups to compare their phenotypic responses
```{r}
#group_v_group(1,4)
```

