---
title: "flowmalizR"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{flowmalizR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

`Flowmalizr` takes an xls input sheet containing columns listed as groups, total_cell_count_per_mL, live_cells, and phenotypes of interest. these contain a group-replicate, 
cell number per mL, live cell count, and cells identified, respectively. 
This is used to detemine cells_from_total and percentage of total by (total_cell_count_per_mL*cells-of-phenotype/live_cells)*100. The output from this 
function is a dataframe that can be manipulated for visualization of cell phenotypes 
from each group.

The rest of this package uses functions as commands to further interpret and visualize the data.

`sep_groups()`

`unique_pops()`

`gg_view_all()`

`visualize_groups()`

`group_v_group(groupA, groupB)`






### Load `flowmalizr()`

```{r setup}
library(flowmalizr)
```

### Read in the raw file and name it as `path_to_data`

```{r}
path_to_data <- system.file("extdata", "example_data.xlsx", package = "flowmalizr")

flowmalizr(path = path_to_data)
```

### Separate group and replicate into their own columns

```{r}
sep_groups()
```

### Pull unique gated populations

```{r}
unique_pops()
```

### Plot percentage of populations per group

```{r, fig.width=9, fig.height=8}
groups <- visualize_groups()
pdf(file="groups.pdf")
plot(groups)
dev.off()
```

### 1v1 comparison: Enter no more than two groups to compare their phenotypic responses. 

```{r, fig.width=9, fig.height=8}
one_v_one_plot <- group_v_group(1,4)


pdf(file="one_v_one_plot.pdf")
plot(one_v_one_plot)
dev.off()

```

